\documentclass[11pt, a4paper]{awesome-cv}

% -----------------------------------------------------------

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}
\usepackage{import}
\usepackage{hyperref}

\newcommand{\checkcase}{sample}
\name{RUMYANA}{ATANASOVA}
%\address{Mountain View, CA 94043}
\mobile{0878984486} 
\homepage{Ruse, Vladaja 8a}

\email{rumyana.yordanova.atanasova@gmail.com}
\linkedin{https://www.linkedin.com/in/rumyana-atanasova/}

\newcommand{\showgrades}{yes}
\ifdefstring{\checkcase}{finance}{\colorlet{awesome}{awesome-darknight}}{\colorlet{awesome}{awesome-red}}

\begin{document}
\makecvheader
\let\cleardoublepage\clearpage
\vspace{+3mm}
\vspace{+3mm}
\vspace{+3mm}
% \import{\sectiondir}{PersonalSummary.tex}
\vspace{-10mm}
\cventryone
{}
{
Reliable, teamwork-oriented physiotherapist with over 25 years of experience in working with patients. I have experience working with patients from diverse medical history, experience with creating and supervising patients' treatment in a team, and experience with managing the medical documentation of my department. 
}
\vspace{+4mm}
% \importsectioncommandtwo{WorkHistory.tex}{Experience}
% ----- Main  ---------


\cventry
{Senior Physiotherapist \textit{at}  Multi-profile Hospital for Active Healthcare - Rousse}
{Ruse, Bulgaria 2008-Present}
{
Working in \textit{Department of Physiotherapy}; main duties performed: 
\newline
\hspace{3ex} - Providing treatment for patients undergoing recovery from a wide range of accidents and surgeries.
\newline
\hspace{3ex} - Examining patients' conditions and establishing a treatment aiming for patients' recovery. 
\newline
\hspace{3ex} - Teaming up with cardiologists, surgeons, orthopedic surgeons, GPs, nurses, consultants and social care workers in order to create treatment strategies for patients. 
\newline
\hspace{3ex} - Working with children over the age of 5 who have a variety of medical conditions such as Cerebral palsy.
\newline
\hspace{3ex} - Helping elderly people to recover from traumas and devising strategies to increase their mobility. Working with nurses, orthopedic technicians and occupational therapists to align with patients' needs of medical equipment. 
\newline
\hspace{3ex} - Liaising patients' treatment with other physiotherapists. Managing the workflow of younger colleagues and overviewing their progress. 
\newline
\hspace{3ex} - Working with specialised physiotherapy equipment and tools like Ultrasound Machines, devices for Magnetic therapy like The Magneto Styms or Magnetic therapy units, Interferential Therapy devices, BTL Shockwave Therapy devices, etc.
\newline
\hspace{3ex} - Examining the quality of treatment for patients in the department.
\newline
\hspace{3ex} - Organizing medical records in the department and reviewing their quality.   
}
\vspace{+3mm}
\cventry
{Physiotherapist \textit{at}  Multi-profile Hospital for Active Healthcare - Rousse}
{Ruse, Bulgaria 1997-2008}
{
Working in \textit{Department of Cardiology}, main duties performed: 
\newline
\hspace{3ex} - Creating and managing rehabilitation programs for patients recovering from cardiovascular diseases.
\newline
\hspace{3ex} - Working with patients recovering from Myocardial Infarction, Angina Pectoris, Hypotension, etc.
\newline
\hspace{3ex} - Creating rehabilitation plans that includes: Healing Physical Therapy, crutch walking exercises, breathing exercises, etc.
}
\vspace{+3mm}
\cventry
{Physiotherapist \textit{at}  Sports Complex Yalta}
{Ruse, Bulgaria 1989-1997}
{
Main duties performed: 
\newline
\hspace{3ex} - Constructing rehabilitation programs for athletes who are undergoing recovery from sports injuries
\newline
\hspace{3ex} - Organizing programs that help children with prophylaxis of Scoliosis.   
\newline
\hspace{3ex} - Supporting athletes' recovery and wellbeing with the help of sauna sessions, underwater rehabilitation gymnastics, 
healing baths, massage therapy, etc.
\newline
\hspace{3ex} - Teaching Pilates and aerobics courses.
\newline
\hspace{3ex} - Building and maintaining exceptional client relationships. Working with clients personally and tracking individual progress. Supervising weekly nutrition and physical activity. Working front desk as well as with clients personally and in group classes. 
}
\vspace{+3mm}
\cventry
{Lab Technician \textit{at} Petroleum Processing Plant "Leon Tadjer"}
{Ruse, Bulgaria 1985-1986}
{
Main duties performed: 
\newline
\hspace{3ex} - Quality control of lubricating oils.
\newline
\hspace{3ex} - Working with oil products and oil refining equipment and tools.
}
% \importsectioncommandtwo{Education.tex}{Education}
\cventry
{Bachelor's degree \textit{at} "Angel Kanchev" University of Ruse}
{Ruse, Bulgaria 2004-2007}
{
Subject: Kinesitherapy and Physiotherapy
\newline
\textit{Courses taken in:} Physiology, Informational analysis of movement, Kinesitherapy in orthopedics orthotics and prosthetics, Kinesitherapy in internal illness, Kinesitherapy in mental and nervous system illness, aerobics and Callanetics, Manual therapy, Kinesitherapy in elderly, reflexotherapy, pharmacy, medical physiology and medical pedagogics.
}

\vspace{+3mm}
\cventry
{Bachelor's degree \textit{at} Medical University Pleven}
{Pleven, Bulgaria 1986-1989}
{
Subject: Physiotherapy
\newline
\textit{Courses taken in:} Anatomy, Biochemistry, Biomechanics and Kinesitherapy, basics of Kinesitherapy, methods and tools, Kinesitherapy and rehabilitation, Sports medicine, specialised rehabilitation methods, refectory massage, Working with medical statistics, kinesitherapy in surgery, obstetrics and gynaecology and Pathology.
}
% \import{\sectiondir}{EducationPageTwo.tex}
\vspace{+3mm}
\cventry
{Secondary education \textit{at} Prof. Dimitar Balarev" High school}
{Ruse, Bulgaria 1982-1985}
{
% Diploma za Sredno Obrazovanie (Bulgaria) 5.55/6.00 - Matura: Bulgarian Language; Matura: English Language, Matura: Maths
Studied in profile specialized in oil and gas refining
}
\vspace{+3mm}
% \importsectioncommandtwo{Languages.tex}{Languages}
\cventrytwo
{
Bulgarian: native language
\newline
Russian: CEFR C2 (Full Proficiency)
% full proficiency (around C2 in CEFR)
\newline
Hebrew: CEFR B1 (Intermediate Level)
\newline
English: CEFR B1 (Intermediate Level)
\newline
German: CEFR A2 (Elementary Level)
}
% \importsectioncommandtwo{ProfessionalTrainingAndQualifications.tex}{professional training and qualifications}
\cventry
{Certificate}
{Sofia, Bulgaria 19.04.2017-21.04.2017}
{
Modern methods of rehabilitation of Nervous system and locomotor apparatus illnesses. Functional electrical stimulation, soft tissue techniques - post-mesmeric relaxation, massage techniques,  traction and mobilization.
}
\vspace{+3mm}
\cventry
{Certificate}
{Ruse, Bulgaria 20.12.2002}
{
Working with computer systems. Working with Microsoft Windows OSes. Working with Microsoft Office Word, Excel, PowerPoint, and working with Internet applications. 
}
% \importsectioncommandthree{Interests.tex}{Interests}
% \cvsection{Interests}
\cventrytwo
{
\begin{cvitemsone}
\item {Gardening and growing flowers.}
\item {Adopting animals and caring for them.}
\item {Playing football, running, gymnastics and other sports.}
\item {Reading, Listening to music and watching classic movies.}
\item {Traveling and meeting with new people.}
\end{cvitemsone}
}

\vspace{+1mm}
% \importsectioncommandthree{References.tex}{References}
\cventrytwo
{Available at request}
\end{document}
